Combat Sandbox

### 2023-10-12 ukb_combat.Rmd
updating to qsub models from multiple .csvs - NEED TO TEST

```{r}
cf.lm_refA <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale, ref.batch = "Site_A")
# cf.lm_refA$dat.combat
```

@@

```{r}
cf.gam_refA <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale, ref.batch = "Site_A")
```

@@

```{r}
cf.gamlss_refA <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE),
              ref.batch = "Site_A")
```

Add back batch and covariance
```{r}
cf.list <- list(cf, cf.lm, cf.lm_refA, cf.gam, cf.gam_refA, cf.gamlss, cf.gamlss_refA)
length(cf.list)

combat.df.list <- lapply(cf.list, post_combat_concat, og_df = ukb_df_sites)
names(combat.df.list) <- c("cf", "cf.lm", "cf.lm_refA", "cf.gam", "cf.gam_refA", "cf.gamlss", "cf.gamlss_refA")
```

write out
```{r}
for (i in names(combat.df.list)){
  df <- combat.df.list[[i]] %>%
  write_csv(df, file=paste0("data/ukb_to_model/ukb_", as.character(i), "_data.csv"))
}
```

@@

```{r}
var_comp_df <- data.frame(sim.site = c("Site_A", "Site_B", "Site_C"),
                          raw_data = sum_df$var.lh_v_sp,
                          cf = cf_summary$var.lh_v_sp,
                          cf.lm = cf.lm_summary$var.lh_v_sp,
                          cf.lm_refA = cf.lm_refA_summary$var.lh_v_sp,
                          cf.gam = cf.gam_summary$var.lh_v_sp,
                          cf.gam_refA = cf.gam_refA_summary$var.lh_v_sp,
                          cf.gamlss = cf.gamlss_summary$var.lh_v_sp,
                          cf.gamlss_refA = cf.gamlss_refA_summary$var.lh_v_sp)

>>>>

```{r}
cf.lm-refA <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale, ref.batch = "Site_A")
# cf.lm-refA$dat.combat
```

@@

```{r}
cf.gam-refA <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale, ref.batch = "Site_A")
```

@@

```{r}
cf.gamlss-refA <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE),
              ref.batch = "Site_A")
```

Add back batch and covariance
```{r}
cf.list <- list(cf, cf.lm, cf.lm-refA, cf.gam, cf.gam-refA, cf.gamlss, cf.gamlss-refA)
length(cf.list)

combat.df.list <- lapply(cf.list, post_combat_concat, og_df = ukb_df_sites)
names(combat.df.list) <- c("cf", "cf.lm", "cf.lm-refA", "cf.gam", "cf.gam-refA", "cf.gamlss", "cf.gamlss-refA")
```

write out
```{r}
for (i in names(combat.df.list)){
  df <- combat.df.list[[i]]
  write_csv(df, file=paste0("data/ukb_to_model/ukb_", i, "_data.csv"))
}
```

@@

```{r}
var_comp_df <- data.frame(sim.site = c("Site_A", "Site_B", "Site_C"),
                          raw_data = sum_df$var.lh_v_sp,
                          cf = cf_summary$var.lh_v_sp,
                          cf.lm = cf.lm_summary$var.lh_v_sp,
                          cf.lm-refA = cf.lm-refA_summary$var.lh_v_sp,
                          cf.gam = cf.gam_summary$var.lh_v_sp,
                          cf.gam-refA = cf.gam-refA_summary$var.lh_v_sp,
                          cf.gamlss = cf.gamlss_summary$var.lh_v_sp,
                          cf.gamlss-refA = cf.gamlss-refA_summary$var.lh_v_sp)
